Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source

### 2018-07-29 main.tex
update

%mm substantive changes marked like this, others made silently

@@

% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
% AE: Had a hard time coming up with a succinct and interesting sounding title that
%     fit both of the interesting results: 
%          1) analytic PDF fits and 2) variations in metal mixing...
\title{Metal Mixing 
%mm 
    and Ejection
in Dwarf Galaxies is Dependent on Nucleosynthetic Source}

@@

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\author{{\it more...}}

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for 
%mm 
    multi-channel 
stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy 
%mm through 
    by
galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal 
%mm + 
   and
power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe). This difference is driven by the differences in 
%mm energetics between each source, particularly the poor coupling of AGB winds to the ISM. 
    source locations, particularly the higher chance compared to massive stars for AGB stars to eject material into cold gas.
Nearly all of the produced metals are ejected from the galaxy (only 5\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

@@

One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references). While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}). Consequently, following metal mixing, if treated in these models, requires assumptions about how metals mix within the ISM and how metals couple to galactic outflows. When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly. However, these processes are critical components in understanding galactic chemical evolution. Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillotta2018}. In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically 
%mm [added Fragile+ 2004 because they studied distributed metal injection.]
\citep[e.g.][]{DekelSilk1986,MacLowFerrara1999,Fragile2004}, 
and with direct observational evidence from the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

@@

In this paper we present the first detailed chemical evolution results from a set of high-resolution hydrodynamics simulations of an isolated, low-mass, dwarf galaxy performed with the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014}. The simulation discussed here was introduced in detail in 
%mm don't forget to introduce into bibliography
Emerick et al.\ (2018; hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB-phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.

The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity. Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging. [list examples of modelling problems]. These uncertainties, combined with the difficulty in simulating a fully self-consistent galaxy in detail, motivates this current study. By focusing on a low mass dwarf galaxy, with small size and low star formation rate, we can capture detailed feedback and ISM physics at high resolution, while following individual stars. In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios, for two reasons. First, we would like to build our understanding of galactic chemical evolution from a fundamental level. Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies 
%mm with observational analogs 
  of easily observable size
in as much detail as done here. This work will be the first of several attempting to bridge this gap. With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and physically motivated sub-grid physics models for lower resolution simulations of more massive galaxies.

We summarize our methods and physics models in Section~\ref{sec:methods}. We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}. In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM. 
%mm
   We discuss our results in Section~\ref{sec:discussion}, and conclude in 
   Section~\ref{sec:conclusions  }.

@@

%mm \textit{Hydrodynamics ---} 
\paragraph{Hydrodynamics} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}. Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers. We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver. We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc. Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas 
%mm and 
    or
2) a cell's local Jeans length becomes resolved by less than eight cells. If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution. At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.

%mm \textit
\paragraph{Chemistry, Heating, and Cooling Physics} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}. We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}. We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely. Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}. Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.

%mm \textit
\paragraph{Star Formation} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$. Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$. Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$). We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%. Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment. We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).

%mm \textit
\paragraph{Stellar Feedback and Stellar Yields} We track the feedback and yields of 15 metal species for each star individually. Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution. Stars above this mass are assumed to direct collapse with no mass or energy injection. For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}. We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars. Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind. Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields. Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et. al. in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.

\paragraph{Initial Conditions} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}. We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$. The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc. Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium. The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy. Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero. Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.

@@

The first core collapse supernova occurs at 12~Myr,

@@

\subsection{Do these results apply to more massive galaxies?}
\label{sec:massive galaxies}
One important caveat about our work is that these results are derived from simulations of an isolated, low mass dwarf galaxy whose properties vary dramatically from a more massive galaxy like the Milky Way. It is unclear how much of these results apply to more massive galaxies given their deeper potential wells and higher star formation rates. Feedback driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas. We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy. With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate. If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform. If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way. This difference would be greater at later times (higher metallicity) once AGB enrichment becomes significant. For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}. At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way. Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way. However, there has been no definitive explanation for these observations. Generalizing our results and detailing their observational consequences is the topic of ongoing work.

>>>>

@@

% GB(AE): Make sure to specify DG in title and at minimum hint at results of paper (include log-normal some how??)
% AE: Had a hard time coming up with a succinct and interesting sounding title that
%     fit both of the interesting results: 
%          1) analytic PDF fits and 2) variations in metal mixing...
\title{Metal Mixing in Dwarf Galaxies is Dependent on Nucleosynthetic Source}

@@

\author{Andrew Emerick}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Greg L. Bryan}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 5th Ave, New York, NY, 10003, U.S.A}
\author{Mordecai-Mark Mac Low}
\affiliation{Department of Astrophysics, American Museum of Natural History, New York, NY, USA}
\author{Benoit C{\^o}t{\'e}}
\affiliation{T.B.D.}
\author{Kathryn V. Johnston}
\affiliation{Department of Astronomy, Columbia University, New York, NY, 10027, USA}
\author{Brian O'Shea}
\affiliation{T.B.D.}

\begin{abstract}
Using a high resolution simulation of an isolated dwarf galaxy, accounting for stellar feedback and chemical evolution on a star-by-star basis, we investigate how each of 15 metal species are distributed within our multi-phase interstellar medium (ISM) and ejected from our galaxy through galactic winds. For the first time, we demonstrate that the mass fraction probability distribution functions (PDFs) of individual metal species in the ISM are well described by a piecewise log-normal + power-law distribution. The log-normal component generally describes gas at lower metal fractions undergoing enrichment towards the mean metal fraction, driven by recent enrichment events in the power-law tail. The PDF properties, and relative significance of these two components, vary within each ISM phase. Hot gas is dominated by recent enrichment, with a significant power-law tail to high metal fractions, while cold gas is dominated by the log-normal component. In addition, elements dominated by asymptotic giant branch (AGB) wind enrichment (such as N and Ba in our model) mix less efficiently than elements dominated by supernova enrichment (such as $\alpha$ elements and Fe). This difference is driven by the differences in energetics between each source, particularly the poor coupling of AGB winds to the ISM. Nearly all of the produced metals are ejected from the galaxy (only 4\% are retained), but metals dominated by AGB enrichment are retained at a fraction of 20\%. In dwarf galaxies, therefore, elements synthesized predominately through AGB winds should be both overabundant and have a larger spread than elements synthesized in either core collapse or Type Ia supernovae. We discuss the observational implications of these results, their potential use in developing improved models of galactic chemical evolution, and their generalization to more massive galaxies.
\end{abstract}

@@

One-zone chemical evolution models often assume instantaneous mixing of metals from recent star formation into gas available for future star formation (references). While this incorrectly assumes that metal mixing in the ISM plays no role in delaying future enrichment in star formation, how to properly account for this process is poorly understood. This is in large part because both these models and large-scale cosmological simulations lack the necessary fidelity to capture the detailed, multi-phase mixing process of metals in the ISM directly. Recent hydrodynamics simulations have employed parameteric models to account for unresolved sub-grid metal mixing (\textit{need references}), which plays an important role in determining the chemical properties of galaxies (\textit{need references}). Consequently, following metal mixing, if treated in these models, requires assumptions in how metals mix within the ISM and how metals couple to galactic outflows. When metals are tracked individually, as opposed to a global metallicity field, their injection, mixing, and outflow properties are often treated uniformly. However, these processes are critical components in understanding galactic chemical evolution. Detailed hydrodynamics simulations incorporating a realistic multi-phase ISM and detailed stellar feedback are required to understand metal mixing and metal outflows \citep[e.g.][]{Armillotta2018}. In addition, it remains to be seen to what degree, if at all, metals of different nucleosynthetic origins may couple differently to the ISM.

The use of low mass dwarf galaxies, both observationally in the Local Group and in theoretical models, has been critical in improving our understanding of galactic chemical evolution. That dwarf galaxies are efficient metal polluters has been demonstrated for some time both theoretically \citep[e.g.][]{DekelSilk1986,MacLowFerrara1999} with direct observational evidence found in the metal retention fractions of Local Group dwarf galaxies \citep[e.g.][]{Kirby2011-metals,McQuinn2015}. It is commonly assumed that all metals couple equally to galactic outflows, however, which may not be a valid assumption if metals of different nucleosynthetic origins couple differently to the ISM \citep{KrumholzTing2018}. Relaxing this assumption has implications for both interpreting observations of stellar abundances in nearby dwarf galaxies and in modeling galactic chemical evolution in both semi-analytic models and lower resolution cosmological simulations. However, testing this assumption has only become possible recently as it requires high resolution, galaxy-scale hydrodynamics simulations that can resolve ISM mixing and self-consistently drive galactic winds through multi-channel stellar feedback.

@@

In this paper we present the first detailed chemical evolution results from a set of high resolution hydrodynamics simulations in the adaptive mesh refinement code \textsc{Enzo} \citep{Enzo2014} of an isolated, low mass dwarf galaxy. The simulation discussed here was first introduced in detail in Emerick et. al. 2018 (hereafter Paper I). To address the outstanding questions discussed above, these simulations follow star formation using individual star particles, including stellar feedback from massive star and AGB phase stellar winds, photoelectric heating, Lyman Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type 1a supernovae. This is in addition to a detailed model for ISM physics using the \textsc{Grackle} library, as discussed below. We show that metals are strongly ejected via galactic winds, but that the retention of metals in the ISM and their mixing through phases varies significantly depending on the production source of the given elemental species. We show how these elements are distributed in the ISM and conclude with a discussion on the implications of these results.

The physical processes that drive galactic chemical evolution are complex, driven by the details of stellar feedback, turbulence and diffusion in a multi-phase ISM, and variations in stellar yields with nucleosynthetic source and stellar metallicity. Uncertainties in each of these processes make reproducing and interpreting observations of gas and stellar abundances challenging. 
%[AE To Do: list examples of modelling problems].
 These uncertainties combined with the difficultly in simulating a fully self-consistent galaxy in detail motivates this current study. By focusing on a low mass dwarf galaxy, we are capable of capturing detailed feedback and ISM physics at high resolution, while following individual stars, due to their small physical scales and low star formation rates. In this work we focus on theoretical quantities, namely the probability density distributions (PDFs) of metals in the ISM as a function of metal mass fraction, rather than the common observables of stellar and gas abundance ratios for two reasons. First, we would like to build our understanding of galactic chemical evolution from a fundamental level. Second, there are currently no direct observational comparisons we can make to galaxies of this size, and it is computationally infeasible to simulate galaxies with observational analogs in as much detail as we provide here. This work will be the first in several in attempting to bridge this gap. With a more fundamental understanding of metal mixing and stellar enrichment in galaxies, we can construct better one-zone chemical evolution models and low resolution simulations of more massive galaxies with physically motivated sub-grid physics models.

We summarize of our methods and physics models in Section~\ref{sec:methods}. We begin our analysis by presenting the only direct observable comparison we can make at this galaxy mass, discussing the metal retention fractions of our galaxy in Section~\ref{sec:ejection}. In Section~\ref{sec:log-normal} we focus on how each of our 15 individual metal species are distributed and evolve within each phase of the ISM.

@@

\textit{Hydrodynamics ---} We use the adaptive mesh refinement astrophysical hydrodynamics and N-body code \textsc{Enzo}\footnote{} \citep{Enzo2014}. Hydrodynamics are solved using a direct-Eulerian piecewise parabolic method and a two-shock approximate Riemann solver with progressive fallback to more diffusive solvers. We include gas self-gravity and evolve collisionless star particles using a particle mesh N-body solver. We use a 128$^{3}$ base grid measuring 2.16~R$_{vir}$ on a side, where R$_{\rm vir}$ = 27.4~kpc, and 8 levels of refinement, for a maximum spatial resolution of 1.8~pc. Refinement occurs when either: 1) a cell contains more than 50~M$_{\odot}$ of gas and 2) a cell's local Jeans length becomes resolved by less than 8 cells. If the cell is within 4 zones of a star particle with active feedback, it is refined to the maximum resolution. At the maximum resolution, we use a pressure floor to prevent artificial fragmentation when the Jeans length is unresolved.

\textit{Chemistry, Heating, and Cooling Physics ---} We use the the astrophysical chemistry and cooling package \textsc{Grackle} \citep{GrackleMethod} to evolve a nine species non-equilibrium primordial chemistry model (including molecular hydrogen), follow approximate metal line cooling using a \textsc{Cloudy} look-up table, and apply heating from a metagalactic UV background \citep{HM2012}. We account for approximate self-shielding of HI against the UV background following \cite{Rahmati2013}. We assume HeI self-shields in the same fashion as HI, and ignore HeII heating from the UVB entirely. Approximate H$_2$ self-shielding from background Lyman-Werner (LW) radiation is accounted for using the Sobolov-like method from \cite{Wolcott-Green2011}. Finally, we use the updated metal line cooling tables which self-consistently account for the decrease in metal line cooling rates due to lower ionization fractions in self-shielding gas, as compared to metal cooling tables computed under the optically thin assumption.

\textit{Star Formation ---} Stars are followed as individual star particles from 1~M$_{\odot}$ to 100~M$_{\odot}$. Stars are able to form in dense gas with: 1) n~$>$~200~cm$^{-3}$, 2) T~$<$~200~K, and 3) $\nabla \cdot v < 0$. Given the short time-steps ($dt \sim 500$~yr) and high resolution (1.8~pc) in these simulations, the local star formation rate in any single zone is very small ($\ll$ 1~M$_{\odot}$ dt$^{-1}$). We therefore form stars stochastically, depending upon the local gas mass, free-fall time, and star formation efficiency, $\epsilon_{\rm f}$, taken to be 2\%. Stellar masses are randomly sampled from an assumed \cite{Salpeter1955} IMF with metallicities and metal fractions set by the local gas environment. We use the zero age main sequence properties of stars from the \textsc{PARSEC} stellar evolution tables \citep{Bressan2012,Tang2014} to determine individual stellar lifetimes and properties which are used to set their LW band, far ultraviolet (FUV) band, and ionizing radiation luminosities (see below).

\textit{Stellar Feedback and Stellar Yields ---} We track the feedback and yields of 15 metal species for each star individually. Stars between 8 M$_{\odot} < M_{*} < 25 M_{\odot}$ explode as core collapse supernovae at the end of their life, injecting their mass and 10$^{51}$~erg of thermal energy into a spherical region with radius of 5.4~pc, or 3 times the maximum resolution. Stars above this mass are assumed to direct collapse with no mass or energy injection. For all stars above 8~M$_{\odot}$ we follow their stellar winds assuming continuous mass loss over their lifetimes, their LW and FUV radiation as optically thin radiation which contributes to H$_2$ dissociation and photoelectric heating respectively, and their HI and HeI ionizing radiation using an adaptive ray-tracing radiative transfer method \citep{WiseAbel2011}. We interpolate over the OSTAR2002 \citep{Lanz2003} grid to set the luminosities of each of these stars. Low mass stars, $M_{*} < 8~M_{\odot}$, do not produce feedback during their main sequence lifetimes, but end their lives injecting a short-lived, low velocity (10 km~s$^{-1}$) AGB wind. Stars with $3 < M_{*,o} < 8$ are tracked after their death as possible Type Ia supernova progenitors, using a delay time distribution model to assign when (if at all) they will explode as a Type Ia, injecting 10$^{51}$~erg of thermal energy with yields. Stellar yields are computed using the NuGrid stellar yield database \citep{Ritter2017} for all stars with $M_{*} < 25~M_{\odot}$, \textbf{Slemer et. al. in prep} for the stellar winds of stars with $M_{*} > 25~M_{\odot}$, and \cite{Thielemann1986} for Type Ia supernovae.

\textit{Initial Conditions ---} Our dwarf galaxy is initialized to approximate, but not reproduce, the $z = 0$ properties of an ultrafaint dwarf galaxy (UFD) as informed by the observed properties of Leo P \citep[see ][]{Giovanelli2013,McQuinn2015a,McQuinn2015}. We initialize a M$_{\rm gas} = 1.8 \times 10^{6}$~M$_{\odot}$ disk as an expotential profile with $Z = 4.3 \times 10^{-4}$ centered on a static \cite{Burkert1995} dark matter potential with M$_{\rm vir} = 2.5 \times 10^{9}$. The gas scale radius and scale height are set to 250~pc and 100~pc respectively, with a maximum radial extent of 600~pc. Both the gas temperatures and velocities are set iteratively to enforce initial hydrostatic equilibrium. The galaxy contains no initial background stellar population, limiting the number of Typa Ia supernovae in our model, but we do provide initial supernova driving to limit the initial transient burst of star formation from the initial cooling and collapse of the galaxy. Although the total metallicity field is initially non-zero, we only track the self-consistently produced metal enrichment for each individual metal species in our simulation, setting their initial abundances to zero. Our analysis is based on the evolution of this galaxy during the first 500~Myr after the formation of the first star particle.

@@

%

@@

\subsection{Do these results apply to more massive galaxies?}
\label{sec:massive galaxies}
One important caveat about our work is that these results are derived from simulations of an isolated, low mass dwarf galaxy whose properties vary dramatically from a more massive galaxy like the Milky Way. It is unclear how much of these results apply to more massive galaxies given their deeper potential wells and higher star formation rates. Feedback driven galactic outflow properties do vary significantly with halo mass \citep[e.g.][]{MacLowFerrara1999,Muratov2017}, as more massive galaxies more easily retain and re-accrete gas. We expect the results presented in Figure~\ref{fig:species_fractions} to be the most susceptible to the particular star formation history and halo depth of a given galaxy. With gas from individual enrichment events more easily contained, we would expect the retention fractions to be more similar across metal species with increasing halo mass or decreasing star formation rate. If true, this difference in metal retention can be a key observable in verifying our result that the dynamical evolution of metals in the ISM is not uniform. If massive galaxies retain metals equally, we would expect dwarf galaxies to exhibit larger abundance ratios between AGB wind elements and SN enriched elements than stars in more massive galaxies, like the Milky Way. This difference would be greater at later times (higher metallicity) once AGB enrichment becomes significant. For example, at metallicities of [Fe/H] $\gtrsim$ 1, Ba is predominantly produced via s-process and ejected in AGB winds \citep{Travaglio1999,Travaglio2004}. At this metallicity, we would expect an elevated [Ba/$\alpha$] at fixed [$\alpha$/H] for low mass dwarfs as compared to the Milky Way. Indeed, this is found in the dSph's of the Milky Way \citep[see ][]{Tolstoy2009} and has been argued to either be the result of variations in s-process enrichment in metal poor environments and/or the result of enrichment timescale differences given the different star formation histories of dwarf galaxies and the Milky Way. In addtion, recent observations find elevationd [Ba/Fe] vs. [Fe/H] in local dwarf galaxies \citep{DugganKirbyAAS},
% AE TODO: Update duggand and kirby if / when the paper comes out
which could possibly be explained by this effect, but could also point towards significant Ba enrichment from NSMs. Given the lack of definitive explanation, clearly generalizing our results and detailing their observational consequences is a valuable area of future research.
